I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-04-27 lipics-master/comppaths.tex
changes

First, notice that by continuity of all the functions used in the DNNs, it suffices to show both theorem for $\gamma=\alpha$ and $\gamma=\beta$.
%Intuitively, our first proof shows that if there are no compensation, then there are no correlations between nodes.
Consider a target neuron $z$.
In case there is no compensating path, we can assign a sign to each neuron $n$: 0
if all paths from $n$ to $z$ has weight 0, $+1$ if all paths have positive weights, and 
$-1$ if they have negative weights. %Using the concept of sign, 
We introduce
% input vectors 
$\vx^{*}, \vx^{\sharp}$:

@@

We can then prove that $\vx^\star,\vx^\sharp$ maximize and minimize conjointly all the nodes in the DNN. Notice that it does {\em not} mean that there is no dependencies between nodes.
There can be correlations between nodes, just they do not affect the $\min$ and $\max$ bounds that can be reached in any node.

\begin{proposition}
	\label{prop.sign}
	${\vx^\star}$ maximizes the value of all positive neurons and minimizes the value of all negative neurons, and  
	${\vx^\sharp}$ minimizes the value of all positive neurons and maximizes the value of all negative neurons.
\end{proposition}

Hence $\val_{\vx^\star}(z)=\beta$ and $\val_{\vx^\sharp}(z)=\alpha$,
for $[\alpha, \beta]$ computed by the Box abstraction. We conclude Theorem \ref{th1} by invocking continuity. The full proof is in appendix A.

>>>>

First, notice that by continuity of all the functions used in the DNNs, it suffices to show both theorem for $\gamma=\alpha$ and $\gamma=\beta$.
%Intuitively, our first proof shows that if there are no compensation, then there are no correlations between nodes.
Consider a target neuron $z$.
In case there is no compensating path, we can assign a "sign" $S(n)$ to each neuron $n$: $S(n)=0$
if all paths from $n$ to $z$ has weight 0, $+1$ if all paths have positive weights, and 
$-1$ if they have negative weights. %Using the concept of sign, 
We introduce
% input vectors 
$\vx^{*}, \vx^{\sharp}$:

@@

We can then prove that $\vx^\star,\vx^\sharp$ maximize and minimize conjointly all the nodes in the DNN. It does {\em not} mean that there is no dependencies between nodes.
There can be correlations between nodes, but they do not affect the $\min$ and $\max$ bounds that can be reached.

\begin{proposition}
	\label{prop.sign}
	${\vx^\star}$ maximizes (${\vx^\sharp}$ minimizes) the value of all positive neurons 
	and minimizes (${\vx^\sharp}$ maximizes) the value of all negative neurons.
\end{proposition}

Hence $\val_{\vx^\star}(z)=\beta$ and $\val_{\vx^\sharp}(z)=\alpha$,
for $[\alpha, \beta]$ computed by the Box abstraction. We conclude Theorem \ref{th1} by invocking continuity. 
Notice that biases have no impact on $S(n)$ (it is {\em not} the sign of )nor the

The full proof is in appendix A.
